### 2014-05-04 docs/seminar/evaluation.tex
minor changes

The coefficient value of Spearman is slightly higher than Kendall's. The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers. Regarding to p-Value of significance test shown in Table~\ref{table:correlation}, a meaningful relation between $GP2$ and feedbacks can be considered. $Top1$ which has the worst values in the table shows a meaningless and near random correlation though.

@@

\begin{table}
\vspace{-0.3cm}
\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
\centering
\begin{tabular}{c c|c|c|c|}
\cline{3-5} & & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.4866 & 0.2295 & 0.05038\\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.5157 & 0.2562 & 0.05263\\
\hline
\end{tabular}
\label{table:correlation}
\vspace{-0.3cm}
\end{table}

>>>>

The outcome shows an approximately weak correlation between aggregation functions and assessments of proof-readers. In all the algorithms, the coefficient value of Spearman is slightly higher than Kendall's. Regarding to p-Value of significance test, a meaningful relation between $GP2$ and assessments can be considered. $Top1$ which has the worst values in the table shows a meaningless and near random correlation though.

@@

\begin{table}
\vspace{-0.3cm}
\centering
\begin{tabular}{c c|c|c|c|}
\cline{3-5} & & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.4866 & 0.2295 & 0.05038\\
\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.5157 & 0.2562 & 0.05263\\
\hline
\end{tabular}
\caption{Correlation test between algorithms and proof-readers' assessments as well as P-Value of significance of correlation test}
\label{table:correlation}
\vspace{-0.3cm}
\end{table}
